---
title: "Tax Bill Tweets Analysis"
author: "Jinghan Cui"
date: "12/18/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
library(ggplot2)
library(tidyr)
library(wordcloud)
library(reshape2)
library(dplyr)
library(ggmap)
```

##1. Overview

The recently released tax bill have raised a big controversy. The objective of my project is to analyze how public comments change over two weeks after the tax bill released. The data is pulled from twitter during the the first week (12.01-12.08) and the second week (12.10-12.18). I use text mining, plotly, sentiment analysis, word clouds and map to show the public attitude's trend over the two weeks.

##2. Method

#### 2.1 Plotly

```{r}
total1_reduced <- readRDS(file = "total1_reduced.rds")
total2_reduced <- readRDS(file = "total2_reduced.rds")
p1 <- ggplot(total1_reduced,aes(x=reorder(words, -n), y=n, fill=n)) +
  geom_col(fill = "steelblue2") +
  theme(axis.text.x=element_text(angle=45, hjust=1, size = 9)) +
  labs(x = "Frequency", y = "Words")

p2 <- ggplot(total2_reduced,aes(x=reorder(words,-n), y=n)) +
  geom_col(fill = "steelblue2") +
  theme(axis.text.x=element_text(angle=45, hjust=1, size = 9)) +
  labs(x = "Frequency", y = "Words")
ggplotly(p1)
ggplotly(p2)
```

#### 2.2 Sentiment Analysis
There are more positive words comparing to the first day. Was the public become more positive to the new tax bill?
```{r}
total1.sentiment <- readRDS(file = "total1.sentiment.rds")
total1.sentiment2 <- readRDS(file = "total1.sentiment2.rds")
total2.sentiment <- readRDS(file = "total2.sentiment.rds")
ggplot(total1.sentiment, aes(date,sentiment)) +
  geom_col(show.legend = FALSE, fill="steelblue2")

total1.sentiment2 %>%
  group_by(sentiment) %>%
  top_n(10,n) %>%
  ungroup() %>%
  mutate(word = reorder(words, n)) %>%
  ggplot(.,aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()

total2.sentiment %>%
  group_by(sentiment) %>%
  top_n(10,n) %>%
  ungroup() %>%
  mutate(word = reorder(words, n)) %>%
  ggplot(.,aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
```

#### 2.3 Word Clouds
```{r}
total1.sentiment2 %>%
  acast(words ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("steelblue2", "tomato3"),
                   max.words = 100)

total2.sentiment %>%
  acast(words ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("steelblue2", "tomato3"),
                   max.words = 100)

```

#### 2.4 Map
```{r}
text.df8.map <- readRDS(file="text.df8.map.rds")
text.df8.map$longitude <- as.numeric(text.df8.map$longitude)
text.df8.map$latitude <- as.numeric(text.df8.map$latitude)
tmp <- get_map(location = text.df8.map, zoom = 5)
ggmap(tmp) +
  geom_point(data=text.df8.map, aes(x=longitude, y= latitude))
```


